Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2018-12-14 Paper.Rmd
mostly working on code for a series of pedagog figs for the sup mat showing the different copulas we use

# Background concepts and methods for Q1: detecting copula structure \label{Methods}

We addressed Q1 in part via a model selection procedure in which the normal copula
and a variety of alternative copulas were fit to 
our ecological datasets, and fits of the various copula models 
were compared via the Akaike and Bayesian 
Information Criteria (AIC and BIC). To make the results more easily interpretable
to readers unfamiliar with copulas, we first introduce the normal copula and 
some alternative copulas we used; and we operationally introduce measures of tail dependence
and asymmetry of tail dependence. 
Additional details are in Appendix \ref{SM-copula_details}. 
Conceptually, a bivariate copula is the same as a probability density function 
on the unit square with uniform maginals. The normal copula family is a one-parameter
family of copulas, with parameter corresponding to the covariance of the related 
bivariate normal distribtion and controlling the degree of dependence 
(Fig. \ref{fig_cop_pedag3}A-B for an example).
Left- and right-tail dependence are $0$ for a the normal copula, and this 
serves as a reference for tail dependence in other copulas. The Clayton and 
survival-Clayton families (Fig. \ref{fig_cop_pedag1}G-H) are two more one-parameter 
families. The Clayton has positive lower-tail dependence ($0.87$ for
the example of Fig. \ref{fig_cop_pedag1}G) and $0$ upper-tail dependence; the 
survival-Clayton, which is a rotation of the Clayton by $180^\circ$, has 
positive upper-tail dependence ($0.87$ in Fig. \ref{fig_cop_pedag1}H)
and $0$ lower-tail dependence. For our model selection procedure (see below), we considered

@@

\begin{figure}[!h]
\begin{center}
\includegraphics[width=3.5in]{./Results/PedagogFig3.pdf}
\caption{Log-transformed pdfs (A, C) and samples from (B, D) example copulas.
Shown are the normal copula with parameter $0.8$ and the Frank copula with 
parameter $10$. See also Fig. \ref{fig_cop_pedag1}E-H for the Clayton and  
survival-Clayton copulas with parameter 5, and Appendix. \label{fig_cop_pedag3}}
\end{center}
\end{figure}

>>>>

# Background, concepts and methods for Q1: detecting copula structure in data \label{Methods}

We addressed Q1 partly via a model selection procedure in which the normal copula
and a variety of alternative copulas were fit to 
our ecological datasets, and fits of the various copula models 
were compared via the Akaike and Bayesian 
Information Criteria (AIC and BIC). To make the results interpretable
to readers unfamiliar with copulas, we first introduce the normal copula and 
some other copulas we used; and we operationally introduce measures of tail dependence
and asymmetry of tail dependence. 
Additional details are in Appendix \ref{SM-copula_details}. 
Conceptually, a bivariate copula is the same as a probability density function 
on the unit square with uniform maginals. The normal copula family is a one-parameter
family of copulas, with parameter corresponding to the covariance of the related 
bivariate normal distribtion, and controlling the degree of dependence 
(Fig. \ref{fig_cop_pedag3}A-B for an example).
Left- and right-tail dependence are $0$ for a the normal copula, and this 
serves as a reference for tail dependence in other copulas. The Clayton and 
survival-Clayton families (Fig. \ref{fig_cop_pedag1}G-H) are two more one-parameter 
families. The Clayton has positive lower-tail dependence ($0.87$ for
the example of Fig. \ref{fig_cop_pedag1}G) and $0$ upper-tail dependence; the 
survival-Clayton, which is a rotation of the Clayton by $180^\circ$, has 
positive upper-tail dependence ($0.87$ in Fig. \ref{fig_cop_pedag1}H)
and $0$ lower-tail dependence. For our model selection procedure (see below), we considered

@@

\begin{figure}[!h]
\begin{center}
\includegraphics[width=3.5in]{./Results/PedagogFig3.pdf}
\caption{Log-transformed pdfs (A, C) and samples from (B, D) example copulas.
Shown are the normal copula with parameter $0.8$ and the Frank copula with 
parameter $10$. See also Fig. \ref{fig_cop_pedag1}E-H for the Clayton and  
survival-Clayton copulas with parameter 5, and Appendix \ref{SM-copula_details}
for additional details. \label{fig_cop_pedag3}}
\end{center}
\end{figure}

### 2018-12-14 SupportingInformation.Rmd
mostly working on code for a series of pedagog figs for the sup mat showing the different copulas we use

```{r cop_pedagog_fig1,echo=F,results="hide"}
set.seed(seed)
source("./FirstPedagogFig.R")
```

@@

>>>>

```{r cop_pedagog_fig1,echo=F,results="hide"}
set.seed(seed)
source("./FirstPedagogFig.R")
source("./ThirdPedagogFig.R")
```

@@

# Transformations used in Fig. \ref{MT-fig_cop_pedag1}

# Background on the copulas we fitted with data \label{copula_details}

<!--****DAN: Need a 10-panel fig for each one-parameter family showing samples and 
pdfs for 5 values of the parameter. May also need something for the two-parameter
families, but not sure yet how to handle it. After doing the univariate families, then
maybe it is enough to show just the pdf, in which case it can be done in a 
5-by-5 array of panels for the 2-parameter families. That seems like it would work.-->
